FraCaS: Temporal Analysis

### 2020-11-11 paper2020/paper.tex
anon
typography

\title{FraCaS: Temporal Analysis}
\author{\authorname{Jean-Philippe Bernardy} \authorname{Stergios Chatzikyriakidis}
  \affiliation{University of Gothenburg}
  \email{firstname.lastname@gu.se}}

@@

In the first premise, our system essentially resolves the ellipsis to
get the following reading: ``ITEL won X orders and APCOM won Y orders
and X > Y.''. One would need each of the verb phrases ``won X orders''
and ``won Y orders'' to introduce their own timespans with existential
quantifiers. However, the organisation of our system is such that the
existentials are introduced before the ellipsis is
expanded. Consequently we get a wrong interpretation and the inference
cannot be made.

>>>>

\title{FraCaS: Temporal Analysis}
\author{\ifanon Anonymous for review\else
  \authorname{Jean-Philippe Bernardy} \authorname{Stergios Chatzikyriakidis}
  \affiliation{University of Gothenburg}
  \email{firstname.lastname@gu.se}\fi}

@@

In the first premise, our system essentially resolves the ellipsis to
get the following reading: ``ITEL won \(X\) orders and APCOM won \(Y\) orders
and $X > Y$.''. One would need each of the verb phrases ``won \(X\) orders''
and ``won $Y$ orders'' to introduce their own timespans with existential
quantifiers. However, the organisation of our system is such that the
existentials are introduced before the ellipsis is
expanded. Consequently we get a wrong interpretation and the inference
cannot be made.
